Bringing the Power of eBPF to Open vSwitch

### 2018-10-24 paper.tex
Edit ch-2.1 section title, ch-2.3

OVS is widely used in virtualized data center environments as a software
switching layer inside various operating systems, including FreeBSD,
Windows Hyper-V, Solaris and Linux. As shown in
Figure~\ref{ovsintro}, the architecture of OVS consists of two major
components: a slow path and a fast path. OVS begins processing packets
in its datapath, the fast path, shortly after the packet is received by the NIC in the host OS.
The OVS datapath first performs packet parsing to extract relevant protocol
headers from the packet and store it locally in a manner that is efficient for
performing lookups (flow key), then it uses this information to look into the
match/action cache (flow table) and determines what needs to be done for this
packet. If there is no match in the flow table, the datapath passes the packet
from the kernel up to the slow path, \verb+ovs-vswitchd+, which maintains the
full determination of what needs to be executed to modify and forward
the packet correctly.  This process is called packet {\em upcall} and
usually happens at the first packet of a flow seen by the OVS datapath.
If the packet matches in this flow table, then the OVS datapath executes its
corresponding actions from the flow table lookup result and updates its flow
statistics.

@@

\subsection{OVS Forwarding Model}

@@

There are several hook points where eBPF programs may be attached in recent
Linux kernels. XDP~\cite{xdp,xdp2} is still an eBPF program, but its attachment point is at the
lowest level of the network stack.  Due to its unique attachment point, the XDP
has its own {\em context}; the input parameters to the XDP eBPF program and return
values have different meanings than the TC eBPF program. XDP shows performance
closed to line rate of the device, because the XDP program is triggered immediately
at the network device driver's packet receiving code path.
Due to its lowest hook point at the networking stack, XDP input parameter has only
pointer to the beginning and end of the packet data plus a few metadatas.
XDP also supports accessing to eBPF maps and tail calls, but with much
less number of helper functions than the eBPF program at TC hook.

Figure~\ref{tcebpf:fig}
shows the typical workflow for installing an eBPF program to the TC/XDP hook point,
and how packets trigger eBPF execution.  Clang and LLVM takes a program
written in C and compiles it down to the eBPF instruction set, then emits an
ELF file that contains eBPF instructions.  An eBPF loader, such as iproute,
takes the ELF file, parses the programs and maps information from it and
issues BPF syscalls to load the program.  If it passes the BPF verifier,
then the program is attached to the hook point (in this case, TC/XDP), and
subsequent packets through the TC/XDP ingress hook will trigger execution of the
eBPF programs.

>>>>

\subsection{OVS Forwarding Model}
OVS is widely used in virtualized data center environments as a software
switching layer inside various operating systems, including FreeBSD,
Windows Hyper-V, Solaris and Linux. As shown in
Figure~\ref{ovsintro}, the architecture of OVS consists of two major
components: a slow path and a fast path. OVS begins processing packets
in its datapath, the fast path, shortly after the packet is received by the NIC in the host OS.
The OVS datapath first performs packet parsing to extract relevant protocol
headers from the packet and store it locally in a manner that is efficient for
performing lookups (flow key), then it uses this information to look into the
match/action cache (flow table) and determines what needs to be done for this
packet. If there is no match in the flow table, the datapath passes the packet
from the kernel up to the slow path, \verb+ovs-vswitchd+, which maintains the
full determination of what needs to be executed to modify and forward
the packet correctly.  This process is called packet {\em upcall} and
usually happens at the first packet of a flow seen by the OVS datapath.
If the packet matches in this flow table, then the OVS datapath executes its
corresponding actions from the flow table lookup result and updates its flow
statistics.

@@

@@

There are several hook points where eBPF programs can be attached in recent
Linux kernels. XDP~\cite{xdp,xdp2} is another eBPF program hook point where
its attachment point is at the lowest level of the network stack.
XDP demonstrates high performance that closed to the line rate of the device,
since the eBPF programs attached to XDP hook point are triggered immediately
in the network device driver's packet receiving code path. For the same reason,
eBPF program in XDP can only access the packet data and a few metadata.
XDP supports accessing to eBPF maps and tail calls, but much less number of
helper functions is available compared to the TC hook point.

Figure~\ref{tcebpf:fig}
shows the typical workflow for installing an eBPF program to the TC/XDP hook point,
and how packets trigger eBPF execution.  Clang and LLVM takes a program
written in C and compiles it down to the eBPF instruction set, then emits an
ELF file that contains eBPF instructions.  An eBPF loader, such as iproute,
takes the ELF file, parses the programs and maps information from it and
issues BPF syscalls to load the program.  If the program passes the BPF verifier,
then it is attached to the hook point (in this case, TC/XDP), and
subsequent packets through the TC/XDP ingress hook will trigger execution of the
eBPF programs.
